---
title: "Data 607 Week 03"
author: "A H M Shahparan"
date: "2/18/2018"
output: html_document
---

## Chapter 8 - Problem 03

###Packages installation
First, we will install the stringr package to convert a string to a vector.
```{r}
library(stringr)
```

###Loading Data
```{r}
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5543642Dr. Julius Hibbert"
#From textbook. Extracts names only.
unformatted_name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
unformatted_name
```
1) Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.
```{r}
formatted_name <- str_replace_all(unformatted_name, '([:graph:]+?), ([:print:]+)', '\\2 \\1')
formatted_name
table1 <- data.frame(unformatted_name,formatted_name)
table1
```

2) Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).
```{r}
with_title <- str_detect(formatted_name, "[[:alpha:]]{2,3}[.]")
table2 <- data.frame(formatted_name,with_title)
table2
```

3) Construct a logical vector indicating whether a character has a second name.
```{r}
with_second_name <- str_detect(unformatted_name," [A-z]{1}\\. ")
table3 <- data.frame(unformatted_name,with_second_name)
table3
```

##Chapter 8 - Problem 04
Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression.

1) [0-9]+\\$
```{r}
#This matches the vector containing strings with continuous numbers followed by a dollar sign at the end. As example:

mixed <- c("How many zeros in 1000000000000000$?")
extracted <- str_match(mixed, '[0-9]+\\$')
extracted
```
2) \\b[a-z]{1,4}\\b
```{r}
#This matches the vector containing strings with one to four continuous lowercase letters surrounded by word edges. As example:
mixed <- c("I am so happy that you showed up. Thank you so much!")
unlist(str_extract_all(mixed, '\\b[a-z]{1,4}\\b'))
```
3) .*?\\.txt$
```{r}
#This matches the vector containing the entirety of any string that concludes with the four characters ‘.txt’. 
mixed <- c("this is not a file.txt", "but this is a file.txt", "this is .txt file")
unlist(str_extract_all(mixed, ".*?\\.txt$"))
```
4) \\d{2}/\\d{2}/\\d{4}
```{r}
#This matches the vector containing strings that have a pattern of two digits, a forward slash, another two digits, another forward slash, and then four more digits.
mixed <- c("12/10/1988 12/100/1988 120/10/1988")
unlist(str_extract_all(mixed, "\\d{2}/\\d{2}/\\d{4}"))
```
5) <(.+?)>.+?</\\1>
```{r}
#This matches the vectors containing strings closed by ending and corresponding closing tags.
exampleE <- c("<head><bold>Testing</bold></>", "<body>Testing 1 2 3...</body>")
unlist(str_extract_all(exampleE, "<(.+?)>.+?</\\1>"))
```

##Chapter 8 - Problem 09
The following code hides a secret message. Crack it with R and regular expressions. Hint: Some of the characters are more revealing than others! The code snippet is also available in the materials at www.r-datacollection.com.
```{r}
secret_code <- 'clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr'
message_found <- unlist(str_extract_all(secret_code, "[[:upper:].!]{1,}"))
message_found
message_found <- str_replace_all(paste(message_found, collapse = ''), "[.]", " ")
message_found
```


